---
title: "Capstone Project"
output:
  html_document:
    df_print: paged
---

```{r}
library(dplyr)
library(ggplot2)
```


```{r}
path = "Data/"
vacant_parcels <- read.csv(paste0(path, "CPAL/DCAD_parcels_vac.csv"), stringsAsFactors = F)
abatement_exempt <- read.csv(paste0(path, "DCAD2019/abatement_exempt.csv"), stringsAsFactors = F)
account_apprl_year <- read.csv(paste0(path, "DCAD2019/account_apprl_year_small.csv"), stringsAsFactors = F)
account_info <- read.csv(paste0(path, "DCAD2019/account_info_small.csv"), stringsAsFactors = F)
account_tif <- read.csv(paste0(path, "DCAD2019/account_tif_small.csv"), stringsAsFactors = F)
account_exempt_value <- read.csv(paste0(path, "DCAD2019/acct_exempt_value_small.csv"), stringsAsFactors = F)
account_exempt_value$ACCOUNT_NUM <- as.character(account_exempt_value$ACCOUNT_NUM)
applied_std_exempt <- read.csv(paste0(path, "DCAD2019/applied_std_exempt_small.csv"), stringsAsFactors = F)
com_detail <- read.csv(paste0(path, "DCAD2019/com_detail_small.csv"), stringsAsFactors = F)
land <- read.csv(paste0(path, "DCAD2019/land_small.csv"), stringsAsFactors = F)
land$ACCOUNT_NUM <- as.character(land$ACCOUNT_NUM)
multi_owner <- read.csv(paste0(path, "DCAD2019/multi_owner_small.csv"), stringsAsFactors = F)
res_addl <- read.csv(paste0(path, "DCAD2019/res_addl_small.csv"), stringsAsFactors = F)
res_detail <- read.csv(paste0(path, "DCAD2019/res_detail_small.csv"), stringsAsFactors = F)
taxable_object <- read.csv(paste0(path, "DCAD2019/taxable_object_small.csv"), stringsAsFactors = F)
taxable_object$ACCOUNT_NUM <- as.character(taxable_object$ACCOUNT_NUM)
taxable_object$TAX_OBJ_ID <- as.character(taxable_object$TAX_OBJ_ID)
```

```{r}
# Join all the files together

df = vacant_parcels %>%
  left_join(account_apprl_year) %>%
  left_join(account_info) %>%
  left_join(account_tif) %>%
  left_join(account_exempt_value) %>%
  left_join(applied_std_exempt) %>%
  left_join(com_detail) %>%
  left_join(land) %>%
  left_join(multi_owner) %>%
  left_join(res_addl) %>%
  left_join(res_detail) %>%
  left_join(taxable_object)

```

```{r}
summary(account_apprl_year)
```


```{r}
# Abatement exempt
# about properties for which abatements have been granted
head(abatement_exempt)
df = abatement_exempt
columns_list = list(apprl_yr = abatement_exempt$APPRAISAL_YR, 
                    tot_val = abatement_exempt$TOT_VAL, 
                    city_eff_yr = abatement_exempt$CITY_EFF_YR, 
                    city_val_dif = abatement_exempt$CITY_VAL_DIF, 
                    cnty_val_dif = abatement_exempt$CNTY_VAL_DIF, 
                    isd_val_dif = abatement_exempt$ISD_VAL_DIF, 
                    coll_val_dif = abatement_exempt$COLL_VAL_DIF, 
                    spec_exemption_pct = abatement_exempt$SPEC_EXEMPTION_PCT, 
                    spec_val_dif = abatement_exempt$SPEC_VAL_DIF, 
                    spec_exemption_amt = abatement_exempt$SPEC_EXEMPTION_AMT)
i = 1
for(column in columns_list){
  name = names(columns_list)[i]
  plot(density(x=column), main = paste("Density Plot of", name))
  
  plot(x=abatement_exempt$TOT_VAL, y = column, main = paste("Scatterplot of tot_val vs", name))
  i = i+1
}


```


```{r}
#Account_apprl_year
# primary or central table in this dataset, it contains summary information about all appraisal accounts.


head(account_apprl_year)
df = account_apprl_year
columns_list = list(apprl_yr = abatement_exempt$APPRAISAL_YR, 
                    tot_val = abatement_exempt$TOT_VAL, 
                    city_eff_yr = abatement_exempt$CITY_EFF_YR, 
                    city_val_dif = abatement_exempt$CITY_VAL_DIF, 
                    cnty_val_dif = abatement_exempt$CNTY_VAL_DIF, 
                    isd_val_dif = abatement_exempt$ISD_VAL_DIF, 
                    coll_val_dif = abatement_exempt$COLL_VAL_DIF, 
                    spec_exemption_pct = abatement_exempt$SPEC_EXEMPTION_PCT, 
                    spec_val_dif = abatement_exempt$SPEC_VAL_DIF, 
                    spec_exemption_amt = abatement_exempt$SPEC_EXEMPTION_AMT)
i = 1
for(column in columns_list){
  name = names(columns_list)[i]
  plot(density(x=column), main = paste("Density Plot of", name))
  
  plot(x=abatement_exempt$TOT_VAL, y = column, main = paste("Scatterplot of tot_val vs", name))
  i = i+1
}


```



```{r}
# account_info
# contains auxiliary data for each appraisal account in Account_Apprl_Year.
```


```{r}
# account_tif
# contains information about appraisal accounts in Tax Increment Finance districts.


```

```{r}
# acct_exempt_value
# contains the value of each exemption granted


```

```{r}
# applied_std_exempt
# contains information about standard exemptions granted.
```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

