---
title: "Capstone Project"
output:
  html_document:
    df_print: paged
---

```{r}
library(dplyr)
library(ggplot2)
```


```{r}
path = "Data/"
vacant_parcels <- read.csv(paste0(path, "CPAL/DCAD_parcels_vac.csv"), stringsAsFactors = F)
abatement_exempt <- read.csv(paste0(path, "DCAD2019/abatement_exempt.csv"), stringsAsFactors = F)
account_apprl_year <- read.csv(paste0(path, "DCAD2019/account_apprl_year_small.csv"), stringsAsFactors = F)
account_info <- read.csv(paste0(path, "DCAD2019/account_info_small.csv"), stringsAsFactors = F)
account_tif <- read.csv(paste0(path, "DCAD2019/account_tif_small.csv"), stringsAsFactors = F)
account_exempt_value <- read.csv(paste0(path, "DCAD2019/acct_exempt_value_small.csv"), stringsAsFactors = F)
account_exempt_value$ACCOUNT_NUM <- as.character(account_exempt_value$ACCOUNT_NUM)
applied_std_exempt <- read.csv(paste0(path, "DCAD2019/applied_std_exempt_small.csv"), stringsAsFactors = F)
com_detail <- read.csv(paste0(path, "DCAD2019/com_detail_small.csv"), stringsAsFactors = F)
land <- read.csv(paste0(path, "DCAD2019/land_small.csv"), stringsAsFactors = F)
land$ACCOUNT_NUM <- as.character(land$ACCOUNT_NUM)
multi_owner <- read.csv(paste0(path, "DCAD2019/multi_owner_small.csv"), stringsAsFactors = F)
res_addl <- read.csv(paste0(path, "DCAD2019/res_addl_small.csv"), stringsAsFactors = F)
res_detail <- read.csv(paste0(path, "DCAD2019/res_detail_small.csv"), stringsAsFactors = F)
taxable_object <- read.csv(paste0(path, "DCAD2019/taxable_object_small.csv"), stringsAsFactors = F)
taxable_object$ACCOUNT_NUM <- as.character(taxable_object$ACCOUNT_NUM)
taxable_object$TAX_OBJ_ID <- as.character(taxable_object$TAX_OBJ_ID)
```

```{r}
# Join all the files together

df = vacant_parcels %>%
  left_join(account_apprl_year) %>%
  left_join(account_info) %>%
  left_join(account_tif) %>%
  left_join(account_exempt_value) %>%
  left_join(applied_std_exempt) %>%
  left_join(com_detail) %>%
  left_join(land) %>%
  left_join(multi_owner) %>%
  left_join(res_addl) %>%
  left_join(res_detail) %>%
  left_join(taxable_object)

```

```{r}
summary(account_apprl_year)
```

 almost all the columns highly correlate with tot_val and are very right skewed

```{r}
# Abatement exempt
# about properties for which abatements have been granted
# head(abatement_exempt)
# # df = abatement_exempt
# columns_list = list(apprl_yr = abatement_exempt$APPRAISAL_YR, 
#                     tot_val = abatement_exempt$TOT_VAL, 
#                     city_eff_yr = abatement_exempt$CITY_EFF_YR, 
#                     city_val_dif = abatement_exempt$CITY_VAL_DIF, 
#                     cnty_val_dif = abatement_exempt$CNTY_VAL_DIF, 
#                     isd_val_dif = abatement_exempt$ISD_VAL_DIF, 
#                     coll_val_dif = abatement_exempt$COLL_VAL_DIF, 
#                     spec_exemption_pct = abatement_exempt$SPEC_EXEMPTION_PCT, 
#                     spec_val_dif = abatement_exempt$SPEC_VAL_DIF, 
#                     spec_exemption_amt = abatement_exempt$SPEC_EXEMPTION_AMT)
# i = 1
# for(column in columns_list){
#   name = names(columns_list)[i]
#   plot(density(x=column), main = paste("Density Plot of", name))
#   
#   plot(x=abatement_exempt$TOT_VAL, y = column, main = paste("Scatterplot of tot_val vs", name))
#   i = i+1
# }
# 

```


```{r}
#Account_apprl_year
# primary or central table in this dataset, it contains summary information about all appraisal accounts.


#head(account_apprl_year)
#df = account_apprl_year

# columns_list = list(impr_val = df$IMPR_VAL,
#   land_val = df$LAND_VAL,
#   tot_val = df$TOT_VAL,
#   hmstd_cap_val = df$HMSTD_CAP_VAL,
#   prev_reval_yr = df$PREV_REVAL_YR,
#   prev_mkt_val = df$PREV_MKT_VAL,
#   city_taxable_val = df$CITY_TAXABLE_VAL,
#   county_taxable_val = df$COUNTY_TAXABLE_VAL,
#   isd_taxable_val = df$ISD_TAXABLE_VAL,
#   hospital_taxable_val = df$HOSPITAL_TAXABLE_VAL,
#   college_taxable_val = df$COLLEGE_TAXABLE_VAL,
#   county_ceiling_value = df$COUNTY_CEILING_VALUE,
#   isd_ceiling_value = df$ISD_CEILING_VALUE,
#   appraisal_meth_cd = df$APPRAISAL_METH_CD
#   )
# 
# i = 1
# for(column in columns_list){
#   name = names(columns_list)[i]
#   gg_df = data.frame(x = column, tot_val = df$TOT_VAL)
#   #print(head(gg_df))
#   print(ggplot(gg_df, aes(x=x, y=tot_val)) + 
#            geom_point() +
#           ggtitle(paste("Scatterplot of", name)))
#   
#   #plot(density(x=column), main = paste("Density Plot of", name))
#   
#   #plot(x=df$TOT_VAL, y = column, main = paste("Scatterplot of tot_val vs", name))
#   i = i+1
# }


```

```{r}
summary(account_info)
```


```{r}
# account_info
# contains auxiliary data for each appraisal account in Account_Apprl_Year.



i = 1
for(column in names(df)){
  print(column)
  name = column
  gg_df = data.frame(x = df[[column]], tot_val = df$TOT_VAL)
  print(head(gg_df))
  print(ggplot(gg_df, aes(x=x, y=tot_val)) + 
           geom_point() +
          ggtitle(paste("Scatterplot of", name)))
  
  #plot(density(x=column), main = paste("Density Plot of", name))
  
  #plot(x=df$TOT_VAL, y = column, main = paste("Scatterplot of tot_val vs", name))
  i = i+1
}
```


```{r}
# account_tif
# contains information about appraisal accounts in Tax Increment Finance districts.


```

```{r}
# acct_exempt_value
# contains the value of each exemption granted


```

```{r}
# applied_std_exempt
# contains information about standard exemptions granted.
```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

