---
title: "Capstone Project"
output:
  html_document:
    df_print: paged
---

```{r}
library(dplyr)
library(ggplot2)
```


```{r}
path = "/Users/tina/Documents/School/Capstone/Dallas Files/"
#vacant_parcels <- read.csv(paste0(path, "CPAL/DCAD_parcels_vac.csv"), stringsAsFactors = F)
abatement_exempt <- read.csv(paste0(path, "DCAD2019/abatement_exempt.csv"), stringsAsFactors = F)
account_apprl_year <- read.csv(paste0(path, "DCAD2020_CURRENT/account_apprl_year.csv"), nrows=10000, stringsAsFactors = F)
account_info <- read.csv(paste0(path, "DCAD2020_CURRENT/account_info.csv"), nrows=10000, stringsAsFactors = F)
account_tif <- read.csv(paste0(path, "DCAD2019/account_tif_small.csv"), stringsAsFactors = F)
account_exempt_value <- read.csv(paste0(path, "DCAD2020_CURRENT/acct_exempt_value.csv"), nrows=10000, stringsAsFactors = F)
account_exempt_value$ACCOUNT_NUM <- as.character(account_exempt_value$ACCOUNT_NUM)
applied_std_exempt <- read.csv(paste0(path, "DCAD2019/applied_std_exempt_small.csv"), stringsAsFactors = F)
#com_detail <- read.csv(paste0(path, "DCAD2019/com_detail_small.csv"), stringsAsFactors = F)
#land <- read.csv(paste0(path, "DCAD2019/land_small.csv"), stringsAsFactors = F)
#land$ACCOUNT_NUM <- as.character(land$ACCOUNT_NUM)
#multi_owner <- read.csv(paste0(path, "DCAD2019/multi_owner_small.csv"), stringsAsFactors = F)
#res_addl <- read.csv(paste0(path, "DCAD2019/res_addl_small.csv"), stringsAsFactors = F)
#res_detail <- read.csv(paste0(path, "DCAD2019/res_detail_small.csv"), stringsAsFactors = F)
#taxable_object <- read.csv(paste0(path, "DCAD2019/taxable_object_small.csv"), stringsAsFactors = F)
#taxable_object$ACCOUNT_NUM <- as.character(taxable_object$ACCOUNT_NUM)
#taxable_object$TAX_OBJ_ID <- as.character(taxable_object$TAX_OBJ_ID)
```

```{r}
# Join all the files together

# df = #vacant_parcels %>%
#   #left_join(account_apprl_year) %>%
#   account_apprl_year %>%
#   left_join(account_info) %>%
#   left_join(account_tif) %>%
#   left_join(account_exempt_value) %>%
#   left_join(applied_std_exempt) %>%
#   left_join(com_detail) %>%
#   left_join(land) %>%
#   left_join(multi_owner) %>%
#   left_join(res_addl) %>%
#   left_join(res_detail) %>%
#   left_join(taxable_object)

```

```{r}
# account_apprl_year X account_exempt
# contains auxiliary data for each appraisal account in Account_Apprl_Year.

df =  account_exempt_value %>%
  left_join(account_apprl_year) 

summary(factor(df$CITY_APPLD_VAL))
summary(df$IMPR_VAL)

df_gg = df %>%
  #filter(!is.na(CITY_APPLD_VAL)) %>%
  filter(IMPR_VAL < 37794550)

#  select(CITY_APPLD_VAL, CNTY_APPLD_VAL, ISD_APPLD_VAL, HOSPITAL_APPLD_VAL, COLLEGE_APPLD_VAL, SPCL_APPLIED_VAL)
summary(factor(df_gg$CITY_APPLD_VAL))
ggplot(df_gg, aes(x=CITY_APPLD_VAL, y = IMPR_VAL, color=CITY_APPLD_VAL, alpha=.5)) +
          geom_point()

df_gg = df %>%
  filter(!is.na(CITY_APPLD_VAL)) %>%
  filter(IMPR_VAL < 2000)

ggplot(df_gg, aes(x=CITY_APPLD_VAL, y = IMPR_VAL, color=CITY_APPLD_VAL, alpha=.5)) +
          geom_point()

```

```{r}
# account_info
# contains auxiliary data for each appraisal account in Account_Apprl_Year.

df = account_apprl_year %>%
  left_join(account_info) 

summary(factor(df$OWNER_CITY))

df_gg = df %>%
  filter(!is.na(OWNER_CITY)) %>%
  filter(IMPR_VAL < 37794550)

#  select(APPRAISAL_YR, DIVISION_CD, BIZ_NAME, OWNER_CITY, OWNER_STATE, OWNER_ZIPCODE, OWNER_COUNTRY, PROPERTY_CITY, PROPERTY_ZIPCODE, MAPSCO, NBHD_CD, LEGAL1, LEGAL2, DEED_TXFR_DATE, LMA, IMA)
summary(factor(df$OWNER_CITY))
ggplot(df_gg, aes(x=TOT_VAL, y = IMPR_VAL, color=OWNER_CITY, alpha=.5)) +
          geom_point()


```

```{r}
head(df)
summary(df)
colSums(is.na(df))
```

There aren't many cities listed. We only want dallas anyways. But there are tons of NA.
```{r}
df_gg = df %>%
  filter(!is.na(PROPERTY_CITY)) %>%
  filter(IMPR_VAL < 37794550)

#  select(APPRAISAL_YR, DIVISION_CD, BIZ_NAME, OWNER_CITY, OWNER_STATE, OWNER_ZIPCODE, OWNER_COUNTRY, PROPERTY_CITY, PROPERTY_ZIPCODE, MAPSCO, NBHD_CD, LEGAL1, LEGAL2, DEED_TXFR_DATE, LMA, IMA)
summary(factor(df$PROPERTY_CITY))
ggplot(df_gg, aes(x=TOT_VAL, y = IMPR_VAL, color=PROPERTY_CITY, alpha=.5)) +
          geom_point()

# see the same for points with <2k improvement value
df_gg = df %>%
  filter(!is.na(PROPERTY_CITY)) %>%
  filter(IMPR_VAL < 2000)

ggplot(df_gg, aes(x=TOT_VAL, y = IMPR_VAL, color=PROPERTY_CITY, alpha=.5)) +
          geom_point()
```

There aren't many zipcodes for us to see 
```{r}
df_gg = df %>%
  filter(!is.na(PROPERTY_ZIPCODE)) %>%
  filter(IMPR_VAL < 37794550)

#  select(APPRAISAL_YR, DIVISION_CD, BIZ_NAME, OWNER_CITY, OWNER_STATE, OWNER_ZIPCODE, OWNER_COUNTRY, PROPERTY_CITY, PROPERTY_ZIPCODE, MAPSCO, NBHD_CD, LEGAL1, LEGAL2, DEED_TXFR_DATE, LMA, IMA)
summary(factor(df$PROPERTY_ZIPCODE))
ggplot(df_gg, aes(x=TOT_VAL, y = IMPR_VAL, color=PROPERTY_ZIPCODE, alpha=.5)) +
          geom_point()

# see the same for points with <2k improvement value
df_gg = df %>%
  filter(!is.na(PROPERTY_ZIPCODE)) %>%
  filter(IMPR_VAL < 2000)

ggplot(df_gg, aes(x=TOT_VAL, y = IMPR_VAL, color=PROPERTY_ZIPCODE, alpha=.5)) +
          geom_point()
```

Res have lower value than commercial

```{r}
df_gg = df %>%
  filter(!is.na(DIVISION_CD)) %>%
  filter(IMPR_VAL < 37794550)

#  select(APPRAISAL_YR, DIVISION_CD, BIZ_NAME, OWNER_CITY, OWNER_STATE, OWNER_ZIPCODE, OWNER_COUNTRY, PROPERTY_CITY, PROPERTY_ZIPCODE, MAPSCO, NBHD_CD, LEGAL1, LEGAL2, DEED_TXFR_DATE, LMA, IMA)
summary(factor(df$DIVISION_CD))
ggplot(df_gg, aes(x=TOT_VAL, y = IMPR_VAL, color=DIVISION_CD, alpha=.5)) +
          geom_point()

# see the same for points with <2k improvement value
df_gg = df %>%
  filter(!is.na(DIVISION_CD)) %>%
  filter(IMPR_VAL < 2000)

ggplot(df_gg, aes(x=TOT_VAL, y = IMPR_VAL, color=DIVISION_CD, alpha=.5)) +
          geom_point()
```

```{r}
df_gg = df %>%
  filter(!is.na(MAPSCO)) %>%
  filter(IMPR_VAL < 37794550)

#  select(APPRAISAL_YR, DIVISION_CD, BIZ_NAME, OWNER_CITY, OWNER_STATE, OWNER_ZIPCODE, OWNER_COUNTRY, PROPERTY_CITY, PROPERTY_ZIPCODE, MAPSCO, NBHD_CD, LEGAL1, LEGAL2, DEED_TXFR_DATE, LMA, IMA)
summary(factor(df$MAPSCO))
ggplot(df_gg, aes(x=TOT_VAL, y = IMPR_VAL, color=MAPSCO, alpha=.5)) +
          geom_point()

# see the same for points with <2k improvement value
df_gg = df %>%
  filter(!is.na(MAPSCO)) %>%
  filter(IMPR_VAL < 2000)

ggplot(df_gg, aes(x=TOT_VAL, y = IMPR_VAL, color=MAPSCO, alpha=.5)) +
          geom_point()

```

```{r}
df_gg = df %>%
  filter(!is.na(NBHD_CD)) %>%
  filter(IMPR_VAL < 37794550)

#  select(APPRAISAL_YR, DIVISION_CD, BIZ_NAME, OWNER_CITY, OWNER_STATE, OWNER_ZIPCODE, OWNER_COUNTRY, PROPERTY_CITY, PROPERTY_ZIPCODE, MAPSCO, NBHD_CD, LEGAL1, LEGAL2, DEED_TXFR_DATE, LMA, IMA)
summary(factor(df$NBHD_CD))
ggplot(df_gg, aes(x=TOT_VAL, y = IMPR_VAL, color=NBHD_CD, alpha=.5)) +
          geom_point()

# see the same for points with <2k improvement value
df_gg = df %>%
  filter(!is.na(NBHD_CD)) %>%
  filter(IMPR_VAL < 2000)

ggplot(df_gg, aes(x=TOT_VAL, y = IMPR_VAL, color=NBHD_CD, alpha=.5)) +
          geom_point()
```

```{r}
df_gg = df %>%
  filter(!is.na(LEGAL1)) %>%
  filter(IMPR_VAL < 37794550)

#  select(APPRAISAL_YR, DIVISION_CD, BIZ_NAME, OWNER_CITY, OWNER_STATE, OWNER_ZIPCODE, OWNER_COUNTRY, PROPERTY_CITY, PROPERTY_ZIPCODE, MAPSCO, NBHD_CD, LEGAL1, LEGAL2, DEED_TXFR_DATE, LMA, IMA)
summary(factor(df$LEGAL1))
ggplot(df_gg, aes(x=TOT_VAL, y = IMPR_VAL, color=LEGAL1, alpha=.5)) +
          geom_point()

# see the same for points with <2k improvement value
df_gg = df %>%
  filter(!is.na(LEGAL1)) %>%
  filter(IMPR_VAL < 2000)

ggplot(df_gg, aes(x=TOT_VAL, y = IMPR_VAL, color=LEGAL1, alpha=.5)) +
          geom_point()
```

```{r}
df_gg = df %>%
  filter(!is.na(LMA)) %>%
  filter(IMPR_VAL < 37794550)

#  select(APPRAISAL_YR, DIVISION_CD, BIZ_NAME, OWNER_CITY, OWNER_STATE, OWNER_ZIPCODE, OWNER_COUNTRY, PROPERTY_CITY, PROPERTY_ZIPCODE, MAPSCO, NBHD_CD, LEGAL1, LEGAL2, DEED_TXFR_DATE, LMA, IMA)
summary(factor(df$LMA))
ggplot(df_gg, aes(x=TOT_VAL, y = IMPR_VAL, color=LMA, alpha=.5)) +
          geom_point()

# see the same for points with <2k improvement value
df_gg = df %>%
  filter(!is.na(LMA)) %>%
  filter(IMPR_VAL < 2000)

ggplot(df_gg, aes(x=TOT_VAL, y = IMPR_VAL, color=LMA, alpha=.5)) +
          geom_point()
```


THERE IS NOTHING TO SEE IN IMA

```{r}
df_gg = df %>%
  filter(!is.na(IMA)) %>%
  filter(IMPR_VAL < 37794550)

#  select(APPRAISAL_YR, DIVISION_CD, BIZ_NAME, OWNER_CITY, OWNER_STATE, OWNER_ZIPCODE, OWNER_COUNTRY, PROPERTY_CITY, PROPERTY_ZIPCODE, MAPSCO, NBHD_CD, LEGAL1, LEGAL2, DEED_TXFR_DATE, LMA, IMA)
summary(factor(df$IMA))
ggplot(df_gg, aes(x=TOT_VAL, y = IMPR_VAL, color=IMA, alpha=.5)) +
          geom_point()

# see the same for points with <2k improvement value
df_gg = df %>%
  filter(!is.na(IMA)) %>%
  filter(IMPR_VAL < 2000)

ggplot(df_gg, aes(x=TOT_VAL, y = IMPR_VAL, color=IMA, alpha=.5)) +
          geom_point()
```

```{r}
df_gg = df %>%
  filter(!is.na(IMA)) %>%
  filter(IMPR_VAL < 2000) 

#  select(APPRAISAL_YR, DIVISION_CD, BIZ_NAME, OWNER_CITY, OWNER_STATE, OWNER_ZIPCODE, OWNER_COUNTRY, PROPERTY_CITY, PROPERTY_ZIPCODE, MAPSCO, NBHD_CD, LEGAL1, LEGAL2, DEED_TXFR_DATE, LMA, IMA)
summary(factor(df$IMA))
ggplot(df_gg, aes(x=TOT_VAL, y = IMPR_VAL, color=IMA, alpha=.5)) +
          geom_point()
```

 almost all the columns highly correlate with tot_val and are very right skewed

```{r}
# Abatement exempt
# about properties for which abatements have been granted
# head(abatement_exempt)
# # df = abatement_exempt
# columns_list = list(apprl_yr = abatement_exempt$APPRAISAL_YR, 
#                     tot_val = abatement_exempt$TOT_VAL, 
#                     city_eff_yr = abatement_exempt$CITY_EFF_YR, 
#                     city_val_dif = abatement_exempt$CITY_VAL_DIF, 
#                     cnty_val_dif = abatement_exempt$CNTY_VAL_DIF, 
#                     isd_val_dif = abatement_exempt$ISD_VAL_DIF, 
#                     coll_val_dif = abatement_exempt$COLL_VAL_DIF, 
#                     spec_exemption_pct = abatement_exempt$SPEC_EXEMPTION_PCT, 
#                     spec_val_dif = abatement_exempt$SPEC_VAL_DIF, 
#                     spec_exemption_amt = abatement_exempt$SPEC_EXEMPTION_AMT)
# i = 1
# for(column in columns_list){
#   name = names(columns_list)[i]
#   plot(density(x=column), main = paste("Density Plot of", name))
#   
#   plot(x=abatement_exempt$TOT_VAL, y = column, main = paste("Scatterplot of tot_val vs", name))
#   i = i+1
# }
# 

```


```{r}
#Account_apprl_year
# primary or central table in this dataset, it contains summary information about all appraisal accounts.


#head(account_apprl_year)
#df = account_apprl_year

# columns_list = list(impr_val = df$IMPR_VAL,
#   land_val = df$LAND_VAL,
#   tot_val = df$TOT_VAL,
#   hmstd_cap_val = df$HMSTD_CAP_VAL,
#   prev_reval_yr = df$PREV_REVAL_YR,
#   prev_mkt_val = df$PREV_MKT_VAL,
#   city_taxable_val = df$CITY_TAXABLE_VAL,
#   county_taxable_val = df$COUNTY_TAXABLE_VAL,
#   isd_taxable_val = df$ISD_TAXABLE_VAL,
#   hospital_taxable_val = df$HOSPITAL_TAXABLE_VAL,
#   college_taxable_val = df$COLLEGE_TAXABLE_VAL,
#   county_ceiling_value = df$COUNTY_CEILING_VALUE,
#   isd_ceiling_value = df$ISD_CEILING_VALUE,
#   appraisal_meth_cd = df$APPRAISAL_METH_CD
#   )
# 
# i = 1
# for(column in columns_list){
#   name = names(columns_list)[i]
#   gg_df = data.frame(x = column, tot_val = df$TOT_VAL)
#   #print(head(gg_df))
#   print(ggplot(gg_df, aes(x=x, y=tot_val)) + 
#            geom_point() +
#           ggtitle(paste("Scatterplot of", name)))
#   
#   #plot(density(x=column), main = paste("Density Plot of", name))
#   
#   #plot(x=df$TOT_VAL, y = column, main = paste("Scatterplot of tot_val vs", name))
#   i = i+1
# }


```

```{r}
summary(account_info)
```




```{r}
# Loop

# i = 1
# for(column in names(df)){
#   print(column)
#   name = column
#   print(length(df[[column]]))
#   print(length(df$OWNER_CITY))
#   gg_df = data.frame(x = df[[column]], OWNER_CITY = df$OWNER_CITY)
# 
#   print(head(gg_df))
#   print(ggplot(gg_df, aes(x=x, y = ..count.., fill=x)) +
#           geom_bar())
#   #print(ggplot(gg_df, aes(x=x, y= ..count..)) +
#   #  geom_bar(aes(fill = OWNER_CITY), position = "dodge") + 
#   #  ggtitle(paste("Scatterplot of", name)))
#   
#   #plot(density(x=column), main = paste("Density Plot of", name))
#   
#   #plot(x=df$TOT_VAL, y = column, main = paste("Scatterplot of tot_val vs", name))
#   i = i+1
# }
```


```{r}
# account_tif
# contains information about appraisal accounts in Tax Increment Finance districts.


```

```{r}
# acct_exempt_value
# contains the value of each exemption granted


```

```{r}
# applied_std_exempt
# contains information about standard exemptions granted.
```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

